A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-25 main.tex
Updates from Overleaf

@@

Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
Bruce Lipton: the biology of belief %信念的力量
placebo effect and the old belief of genetic determinism\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。
genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
The genetics of the cell give us all kinds of potentials. % 自性空

>>>>

\subsubsection{TCPA validation}
TCGA pathology Deep learning TCPA
數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。

https://www.cancer.gov/research/areas/diagnosis/artificial-intelligence
% NCI
NCI:

Aiding the Genomic Characterization of Tumors

AI methods can also be used to identify specific gene mutations from tumor pathology images instead of using traditional genomic sequencing. For instance, NCI-funded researchers at New York University used deep learning (DL) to analyze pathology images of lung tumors obtained from The Cancer Genome Atlas. Not only could the DL method accurately distinguish between two of the most common lung cancer subtypes, adenocarcinoma and squamous cell carcinoma, it could predict commonly mutated genes from the images.

Understanding the Method Behind the Machine

One challenge of AI, and DL specifically, is the “black box” problem: not fully understanding what features of the data a computer has used in its decision-making process. For example, a DL algorithm that predicts the optimal treatment for a patient does not provide the reasoning it used to make that prediction. Additional efforts are needed to reveal how algorithms arrive at a decision or prediction so that the process becomes transparent to scientists and clinicians. Making these algorithms transparent could help researchers identify new biological features relevant to disease diagnosis or treatment.

Incorporating information about biological processes into the algorithm is likely to improve its accuracy and decrease dependence on large amounts of annotated data, which may not be available. One danger of the “black box” problem is that DL may inadvertently perpetuate existing unconscious biases. Researchers need to carefully consider how potential biases affect the data being used to develop a model, adopt practices to address and monitor those biases, and monitor performance and applicability of AI models.

With increased investments, NCI’s efforts to realize AI’s potential will lead to more accurate and rapid diagnoses, improved clinical decision-making, and, ultimately, better health outcomes for patients with cancer and those at risk.

Updated: August 31, 2020
%
TMA by deep learning (CNN) mRNA expression associated with pathological images

recurrent neural network for NLP
%氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。

@@

Epigenetics control says that genetic expression is directly due to the environment and our perception of the environment\cite{Gustafson2017}.
The microenvironment of HNSCC requires further exploration and understanding using a multiparametric approach.
Bruce Lipton: the biology of belief %信念的力量
placebo effect and the old belief of genetic determinism\cite{Mokhtari2011}\cite{Kobisi2012}\cite{Gustafson2017}
%biowell 勿膨脹自我: 我非常擔心，所謂的科學實驗，研究的疾病，發明的藥物，都會潛藏一種危機，因為它的療效與科學證據，都是建立在「意識統一場域」中，科學家在研究時，一定希望有效，能夠發現別人沒有發現且有用的事情，所以「成功」還是會帶有「人為的意念」。
%那麼，這個結果不「公正」。甚至，當原來藥物發明者的心念改變了，（開始只想賺錢），那麼藥物的作用就更無法掌握。也許，藥物副作用會很嚴重。而目前科學的解釋是，只是因為個體的基因差異。

%% 1. Kobisi, W. Mind inhibitors. in The 30th International Congress Of The World Federation Of Hemophilia, July 8‐12 vol. 18 170–171 (John Wiley & Sons, Ltd, 2012).
As a person with hemophilia (PWH), my passion led me to conduct personal research to uncover the main cause of my drawbacks in my education, my career, and my romantic life. I have experienced unjustified conflicts in my social relations, feeling stale in mind and body, indefinite self-image, emotional instability, and successive spontaneous bleeds despite the continuous factor replacement. My research is based on my experience of living with hemophilia for 37 years, reading countless books on personal development and the mind-body relationship, and having profound discussions about these experiences with my wife. Findings: Through my research, I uncovered that I used to suffer from what I call 'mind inhibitors' these were the hidden cause of my life disorders and spontaneous bleeds. These mind inhibitors are responsible for locking the body factor receptors, blocking body energy centres (like the solar plexus), discouraging the super-intelligent body cells from running their auto-healing system, and paralyzing the instinctive high-speed cellular response to external molecular treatment. Mind inhibitors originate from different sources like thinking of oneself in a victim role, anxiety about medical treatments, lack of financial stability, negative attitudes, self-rejection, and contradictory thoughts and feelings. Conclusion: Mind inhibitors should be handled as seriously as biological inhibitors. As Dr. Bruce Lipton explains in his book, 'The Biology of Belief': DNA does not control our biology; instead DNA is controlled by signals from outside the cell. Our bodies can be changed as we retrain our thinking, since thoughts are made of energy that affects the cellular energy level, and thus everything is created twice: once in our minds and then the physical creation follows. New holistic approaches should be considered for treating PWH as a complete synchronized system of Soul, Mind, and Body; treatment should include more than just factor adjustment. Factor adjustment only treats symptoms, but a holistic approach would also address the patient's need for a subconscious paradigm shift in the person's thought and belief system.\cite{Kobisi2012}

%%

genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
The genetics of the cell give us all kinds of potentials. % 自性空
